---
title: "Alone"
author: "Braden Buchanan"
date: "2023-01-23"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading data
```{r}
survivalists <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-24/survivalists.csv')
loadouts <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-24/loudouts.csv')
episodes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-24/episodes.csv')
seasons <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-24/seasons.csv')
```

# Get the Data

# Read in with tidytuesdayR package 
# Install from CRAN via: install.packages("tidytuesdayR")
# This loads the readme and all the datasets for the week of interest

# Either ISO-8601 date or year/week works!
```{r}
install.packages("tidytuesdayR")
library(tidytuesdayR)
tuesdata <- tidytuesdayR::tt_load('2023-01-24')
tuesdata <- tidytuesdayR::tt_load(2023, week = 4)
```

```{r}
library(tidyverse)
library(psych)
```

EDA
```{r}
tuesdata$survival
view(tuesdata$survivalists)
survival <- tuesdata$survival
```

Reason category most people dropped out
```{r}
survival %>%
  filter(!is.na(reason_category)) %>%
  arrange(reason_category) %>%
  select(reason_category) %>%
  count(reason_category, sort = T) %>%
  ggplot(aes(reason_category, n, fill = reason_category)) +
  geom_col() +
  labs(title = "Biggest reason category for dropping off",
       y = "Number",
       x = "") +
  geom_text(aes(label = n), vjust = -1) +
  theme(panel.background = element_blank(),
        plot.title = element_text(hjust=0.5, face = "bold"))
```

Who got first from each season
```{r}
survival %>%
  filter(result == 1) %>%
  select(gender, profession, result, season)
```

Reasons why second place tapped out
```{r}
survival %>%
  filter(result == 2) %>%
  select(gender, profession, result, season, reason_tapped_out)
```

Most common reasons for tapping out
```{r}
survival %>%
  filter(!is.na(reason_tapped_out)) %>%
  arrange(reason_tapped_out) %>%
  count(reason_tapped_out, reason_category,sort = TRUE) %>%
  head(6) %>%
  ggplot(aes(reason_tapped_out, n, fill = reason_category)) +
  geom_col() +
  labs(title = "Most common reasons for tapping out",
       y = "Number",
       x = "Reason tapped out") +
  geom_text(aes(label = n), hjust = -1) +
  theme(panel.background = element_blank(),
        plot.title = element_text(hjust=0.5, face = "bold")) +
  coord_flip()
```

Average days lasted for first place?
```{r}
(days_lasted <- survival %>%
  filter(result == 1) %>%
  arrange(desc(days_lasted)) %>%
  select(season, result, days_lasted) %>%
  mutate(Average_days_first_place = mean(days_lasted)))

days_lasted %>%
  ggplot(aes(season, days_lasted)) +
  geom_line()
```
